Binary companions of red giant stars in \apogee\ \DR: \\ Search method and catalog of $>$4,500 systems

### 2018-03-09 paper/1-catalog/twoface-catalog.tex
some words and captions

\begin{table}
    \centering
    \begin{tabular}{c | c}
    \texttt{APOGEE\_ID} & \texttt{lnK\_per\_1} \\
    \hline
    2M00000002+7417074 & -2.028 \\
    2M00000068+5710233 & -2.600 \\
    2M00000222+5625359 &  2.134 \\
    2M00000446+5854329 & -7.199 \\
    ... & ...
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s for all \nstars\ stars
    in the parent sample used in this work, for which we have posterior
    samplings in orbital parameters.
    The other column contains the 1st percentile computed over the $\ln K$
    samples for each source, \texttt{lnK\_per\_1}:
    The ``high-$K$'' sample (see \sectionname~\ref{sec:catalog-confident}) is
    defined using this column, by selecting \texttt{lnK\_per\_1 > 0}.
    }
    \label{tbl:lnK-per}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{c | c | c | c | c | c | c}
    \texttt{APOGEE\_ID} & \texttt{P} & \texttt{e} & \texttt{K} &
        \texttt{M1} & \texttt{M2\_min} & \texttt{clean\_flag} \\
    & $\mathrm{d}$ & & $\mathrm{km\,s^{-1}}$ &
        $\mathrm{M_{\odot}}$ & $\mathrm{M_{\odot}}$ &  \\
    \hline
    2M21362657-0017579 & 14.639 & 0.1171 & 30.68 & -- & -- & 0 \\
    2M21362657-0017579 & 2.3049 & 0.0026 & 28.69 & -- & -- & 0 \\
    2M03180303-0004215 & 35.553 & 0.1302 & 4.541 & 1.20 & 0.20 & 0 \\
    2M03180303-0004215 & 107.22 & 0.3192 & 8.792 & 1.20 & 0.13 & 0 \\
    ... & ... & ... \\
    \multicolumn{6}{c}{\textit{(210 rows)}}
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s and limited orbital
    parameter information for all \nbimodal\ stars identified as having bimodal
    posterior samplings in orbital period.
    Each source is listed twice, with MAP values of period, \texttt{P},
    eccentricity, \texttt{e}, and velocity semi-amplitude, \texttt{K}, from each
    period mode of the posterior sampling for the source.
    When available, this table also includes point-mass estimates of the primary
    mass, \texttt{M1}, from \citet{Ness:2015}, and minimum companion masses,
    \texttt{M2\_min}, computed for each period mode.
    }
    \label{tbl:highK-bimodal}
\end{table}

@@

Most of the companions we find have minimum masses $M_{2, \textrm{min}} <
1~\Msun$.
\figurename~\ref{fig:mass}, left panel shows primary and companion mass
estimates for systems with unimodal (black markers) and bimodal (blue lines)
period samplings using primary masses from \citet{Ness:2015}.
Upper dashed line shows the $M_{2, \textrm{min}} = M_1$ line, and lower dashed
line shows the Hydrogen-burning limit, $M_{2, \textrm{min}} = 0.08~\msun$.
For the systems with bimodal samplings, we compute the minimum companion mass
for each period mode and connect these estimates with a line.
Three interesting systems are immediately obvious: two systems with bimodal
period samplings in which both period modes put the minimum companion mass below
the Hydrogen-burning limit, and one system in which $M_{2, \textrm{min}} > M_1$.

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{mass}
\end{center}
\caption{%
TODO
\label{fig:mass}
}
\end{figure}

\subsubsection{2M04582049+2232000}
% BD candidate

\subsubsection{2M20130687+2044173}
% BD candidate

\subsubsection{2M01231070+1801407}
% NS/BH candidate

@@

\figurename~\ref{fig:unimodalPe} shows the orbital period and eccentricity...

\todo{Period - eccentricity plot? Tidal circularization (See "Debug MCMC
continue")}

\todo{eccentricity distribution w/ prior over-plotted}

% Notebook: HighK-unimodal
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{unimodal-P-e}
\end{center}
\caption{%
TODO:
\label{fig:unimodalPe}
}
\end{figure}

\subsection{Eclipsing}

\todo{Stars with Kepler light curves}

@@

\todo{comment on short period shit, eccentricities}

@@

\section{Example data and orbit samples}

>>>>

@@

@@

Most of the companions we find have minimum masses $M_{2, \textrm{min}} <
1~\msun$.
\figurename~\ref{fig:mass}, left panel shows primary and companion mass
estimates for systems with unimodal (black markers) and bimodal (blue lines)
period samplings, again using primary masses from \citet{Ness:2015}.
Upper dashed line shows the $M_{2, \textrm{min}} = M_1$ curve, and lower dashed
line shows the Hydrogen-burning limit, $M_{2, \textrm{min}} = 0.08~\msun$.
For the systems with bimodal samplings, we compute the minimum companion mass
for each period mode and connect these estimates with a line.

\figurename~\ref{fig:mass}, right panel shows the ratio of the primary stellar
radius to the projected separation of the two bodies, $R_1 / (a\,\sin i)$, and
the minimum mass ratio, $q_{\textrm{min}} = M_{2, \textrm{min}} / M_1$, for the
same samples.
Again, black large markers indicate systems from the unimodal sample, and blue
markers and lines connect the two estimates for systems with bimodal period
samplings.
Upper dashed line in this panel indicates the Roche radius, computed using an approximate functional form (\citealt{Eggleton:1983})
\begin{equation}
    \frac{R}{a} = \frac{0.49\,q^{-2/3}}{0.6\,q^{-2/3} +
        \ln\left(1 + q^{-1/3}\right)} \quad .
\end{equation}
All of these systems are generally consistent with being detached binaries.

In \figurename~\ref{fig:mass}, three interesting systems are immediately
obvious: two systems with bimodal period samplings in which both period modes
put the minimum companion mass below the Hydrogen-burning limit, and one system
in which $M_{2, \textrm{min}} > M_1$; We discuss these systems below

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{mass}
\end{center}
\caption{%
\textit{Left panel:} Estimated minimum companion mass and primary mass for
systems in the high-$K$, unimodal sample (black markers) and bimodal sample
(blue markers and lines).
Lines connecting markers (blue) show estimates from each period mode for each
system with bimodal period samplings.
Upper, dashed line shows the equal-mass curve, and lower dashed line shows the
Hydrogen-burning limit.
\textit{Right panel:} Ratio of primary stellar radius, $R_1$, to projected
separation of the two bodies, $a\,\sin i$, and minimum mass ratio,
$q_{\textrm{min}}$, again for systems in the high-$K$, unimodal sample
(black markers) and bimodal sample (blue markers and lines).
\label{fig:mass}
}
\end{figure}

\subsubsection{2M04582049+2232000 -- brown dwarf companion candidate}
% BD candidate

\todo{What to show?}

\subsubsection{2M20130687+2044173 -- brown dwarf companion candidate}
% BD candidate

\todo{What to show?}

\subsubsection{2M01231070+1801407 -- black hole companion candidate}
% NS/BH candidate

\todo{What to show?}

@@

\figurename~\ref{fig:PeK}, left panel, shows the normalized orbital period and
eccentricity for all systems in the high-$K$, unimodal sample, and, right panel,
the RV semi-amplitude.
We normalize the inferred periods by the orbital period of a companion at the
surface of the primary, $P_{\textrm{surface}}$:
To do this for all systems in this sample, we assume that all primary stars have
masses equal to the median mass over all stars with prior mass measurements in
this sample, $M_1 = 1.36~\msun$, and assume a companion mass also equal to the
median over minimum companion masses $M_{2, \textrm{min}} = 0.5~\msun$.
We then use the surface gravity, $\log g$, of the primary, and eccentricity to
compute
\begin{align}
    P_{\textrm{surface}} &= \frac{2\pi \, G^{1/4}}{(1-e)^{-3/2}} \,
        \left(\frac{M_1 + M_2}{M_1^{3/4}}\right) \,
        10^{-3/4\,\log g} \\
    &= XX ...
\end{align}
where we use $M_{2, \textrm{min}}$ as $M_2$.
There is a clear signature of circularization just under $P/P_{\textrm{surface}}
\approx 10$.
\todo{why is this novel with a large sample of giant stars}

% Notebook: Results
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{P-e-K}
\end{center}
\caption{%
TODO:
\label{fig:PeK}
}
\end{figure}

% Notebook: Results
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{ecc-dist}
\end{center}
\caption{%
TODO:
\label{fig:ecc}
}
\end{figure}

% \subsection{Eclipsing}
%
% \todo{Stars with Kepler light curves}

@@

\todo{comment on short period shit at low logg, eccentricities}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{c | c}
    \multicolumn{2}{c}{\textbf{Parent sample of \apogee\ \DR\ stars}}\\
    \hline
    \texttt{APOGEE\_ID} & \texttt{lnK\_per\_1} \\
    \hline
    2M00000002+7417074 & -2.028 \\
    2M00000068+5710233 & -2.600 \\
    2M00000222+5625359 &  2.134 \\
    2M00000446+5854329 & -7.199 \\
    ... & ... \\
    \hline
    \multicolumn{2}{c}{\textit{(\nstars\ rows)}}
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s for all \nstars\ stars
    in the parent sample used in this work, for which we have posterior
    samplings in orbital parameters.
    The other column contains the 1st percentile computed over the $\ln K$
    samples for each source, \texttt{lnK\_per\_1}:
    The ``high-$K$'' sample (see \sectionname~\ref{sec:catalog-confident}) is
    defined using this column, by selecting \texttt{lnK\_per\_1 > 0}.
    }
    \label{tbl:lnK-per}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{c | c | c | c | c | c | c}
    \multicolumn{7}{c}{\textbf{High-$K$, bimodal systems}}\\
    \hline
    \texttt{APOGEE\_ID} & \texttt{P} & \texttt{e} & \texttt{K} &
        \texttt{M1} & \texttt{M2\_min} & \texttt{clean\_flag} \\
    & $\mathrm{d}$ & & $\mathrm{km\,s^{-1}}$ &
        $\mathrm{M_{\odot}}$ & $\mathrm{M_{\odot}}$ &  \\
    \hline
    2M21362657-0017579 & 14.639 & 0.1171 & 30.68 & -- & -- & 0 \\
    2M21362657-0017579 & 2.3049 & 0.0026 & 28.69 & -- & -- & 0 \\
    2M03180303-0004215 & 35.553 & 0.1302 & 4.541 & 1.20 & 0.20 & 0 \\
    2M03180303-0004215 & 107.22 & 0.3192 & 8.792 & 1.20 & 0.13 & 0 \\
    ... & ... & ... \\
    \hline
    \multicolumn{6}{c}{\textit{(210 rows)}}
    \end{tabular}
    \caption{This table contains \texttt{APOGEE\_ID}'s and limited orbital
    parameter information for all \nbimodal\ stars identified as having bimodal
    posterior samplings in orbital period.
    Each source is listed twice, with MAP values of period, \texttt{P},
    eccentricity, \texttt{e}, and velocity semi-amplitude, \texttt{K}, from each
    period mode of the posterior sampling for the source.
    When available, this table also includes point-mass estimates of the primary
    mass, \texttt{M1}, from \citet{Ness:2015}, and minimum companion masses,
    \texttt{M2\_min}, computed for each period mode.
    }
    \label{tbl:highK-bimodal}
\end{table}
